%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awesome Cover Letter
% XeLaTeX Template
% Version 1.3 (30/3/2020)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original authors:
% Claud D. Park (posquit0.bj@gmail.com)
% Lars Richter (mail@ayeks.de)
% With modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template must be compiled with XeLaTeX, the below lines will ensure this
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{awesome-cv} % A4 paper size by default, use 'letterpaper' for US letter

\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} % Configure page margins with geometry
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-nephritis} % Default colors include: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%\definecolor{awesome}{HTML}{CA63A8} % Uncomment if you would like to specify your own color

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} % If you would like to change the social information separator from a pipe (|) to something else

%----------------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%----------------------------------------------------------------------------------------

\name{Joshua}{Limbrey}

\email{joshua@supinie.mozmail.com}
\github{supinie}

\position{Information Security{\enskip\cdotp\enskip}Cryptography{\enskip\cdotp\enskip}Software Dev} % Your expertise/fields

%----------------------------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%----------------------------------------------------------------------------------------

\recipient{WithSecure}{} % The company being applied to

\letterdate{\today} % The date on the letter, default is the date of compilation

\lettertitle{Linux Engineer} % The title of the letter

\letterclosing{Sincerely,} % How the letter is closed

\makecvfooter{\today}{Joshua Limbrey~~~·~~~Cover Letter}{} % Specify the letter footer with 3 arguments: (<left>, <center>, <right>), leave any of these blank if they are not needed
  
%----------------------------------------------------------------------------------------

\begin{document}

\makecvheader % Print the header

\makelettertitle % Print the title

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\begin{cvletter}

%------------------------------------------------

\lettersection{$\sim$/about\_me/}

As a highly skilled technical problem solver with a proven track record of achieving the highest performance, I am excited to apply for a role as an Linux engineer. I thoroughly enjoy pushing systems to their limits, finding loopholes, and understanding the inner workings of all things as if they were a puzzle. I have demonstrated my ability to create innovative solutions to complex problems and challenges, driving the deployment of AWS services into 5 new regions, in addition to updating the build process to include robust automation; setting the standard for service wide automation. 

I have a strong background in mathematics, specifically in public key cryptography, writing my MSc thesis on the hardness of post-quantum schemes; as well as a passion and competency in offensive security and computer science, achieving First Class and distinction in my BSc and MSc respectively.

%------------------------------------------------

\lettersection{$\sim$/why\_WithSecure/}

I believe that WithSecure will provide me with: problems that will challenge and stimulate me, a group of highly capable and like-minded colleagues to work alongside, and an environment in which I will be able to flourish and excel. I believe that my own personal values of privacy and security as a fundamental right strongly aligns with the mission and purpose of WithSecure, and that this job will enable me to not only greatly enjoy the work that I will be doing, but allow me to contribute in a meaningful manner to an area in which I am so enthusiastic about; and to tackle problems that are not only new to me but novel problems being solved for the first time; an idea that I find truly exciting.

%------------------------------------------------

\lettersection{$\sim$/why\_me/}

I thrive in a team environment and am motivated to improve efficiency and tackle issues with the support of a stimulating and highly capable team. My analytical and critical thinking skills, coupled with my aptitude for effective communication, allow me to engage with my team members and make significant and insightful contributions.

I am confident that my experience and skills make me an excellent candidate for this position, and with my academic and work experience combined I will be able to provide a well rounded, capable and adept addition to this team and WithSecure's work. 

Thank you for considering my application.

%------------------------------------------------

\end{cvletter}

%----------------------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}