
%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{$\sim$/experience/}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Principal Full Stack Developer} % Job title
{Supinie Solutions LTD} % Organization
{London, UK} % Location
{Jun. 2022 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Understanding a problem brief, designing and architecting a full-stack solution built in AWS whilst working closely with a number of customers to deliver a tailored solution via an agile workflow.}
\item {Implementing a secure user accounts system, including organisation management and access control.}
\item {Implementing strong logical separation between components alongside rigerous access management controls to ensure best security practices are met.}
\item {Implementing back end databases, as well as dependable integration with external APIs.}
\item {Utilising agile workflow methods to ensure development time is properly spent, and ensuring all customer expectations are met, and exceeded.}
\item {Utilising strong CI/CD principles to ensure early problem discovery, high productivity, and faster release cycles.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{System Development Engineer} % Job title
{Amazon Web Services} % Organization
{Reading, UK} % Location
{Sep. 2022 - Jun. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {A key member of a small team that built AWS Service Catalog into 6 new regions, personally owning a number of internal component services.}
\item {Worked to update the region build process to implement robust automation to cut down engineering hours by a factor of 10.}
\item {Insisted on the highest standards when delivering, setting the standard for many implementations of automation.}
\item {Hands on experience maintaining global services, ensuring the best and smoothest customer experience.}
\item {Owned the full software lifecycle from development, through deployment, to supporting production via CI/CD.}
\item {Ensured that the team met c-level deadlines that otherwise would not have been met; through driving and owning build processes.}
\item {Created new training materials and led engineering development days and experience exchanges amongst ~50 engineers as a subject matter expert.}
\item {Created and developed a new collection of tools and scripts to aid engineering workflows within AWS and Service Catalog.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Dev.} % Job title
{Cyber Software Development} % Organization
{London, UK} % Location
{Jun. 2021 - Sep. 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed a unique covert communication capability utilising decentralised peer-to-peer communications.}
\item {Full stack web-dev.}
\item {Worked with Node.JS back-end and Svelte front-end.}
\end{cvitems}
}

%------------------------------------------------    
\cventry
{Summer Online Learning} % Job title
{Immersive Labs} % Organization
{London, UK} % Location
{Jun. 2020 - Aug. 2020} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Conducted self-driven learning through engagement with Immersive Labs.}
\item {Focus on conducting attacks and offensive techniques.}
\item {Topics covered included:}
\begin{multicols}{3}
\begin{itemize}
    \item Network enumeration
%    \item Enumeration
    \item Credential cracking
    \item Malware
    \item Privilege escalation
    \item Service exploitation
%    \item Web app hacking
    \item IoT/Embedded systems
\end{itemize}
\end{multicols}
\end{cvitems}
}

%------------------------------------------------    
\cventry
{Student} % Job title
{Cyber Summer School} % Organization
{London, UK} % Location
{Jun. 2019 - Aug. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Covered a wide range of topics: 
% \begin{multicols}{2}
\begin{itemize}
    \item Network structure and protocols
    \item SCADA (supervisory control and data acquisition) systems
    \item Cryptography
    \item Programming and scripting
\end{itemize} 
% \end{multicols}
allowing me to build a broad and robust understanding of many key areas of computer systems.}
\item {Worked with TCP/IP and OSI models to conduct packet analysis and network monitoring utilising a wide range of tools giving me a strong understanding of networking protocols and how they work.}
\item {Conducted analysis of SCADA systems using PLCs (programmable logic controllers) to write my own ladder logic program to automatically complete tasks in an ICS (industrial control system). This furthered my understanding and knowledge surrounding these systems as well as my fluency in using them.}
\end{cvitems}
}

%------------------------------------------------    
\cventry
{Intern} % Job title
{International Supply Chain Company} % Organization
{Guangzhou, China} % Location
{Jun. 2016 - Jul. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Worked in various industrial settings and gained exposure to multiple manufacturing processes and quality control techniques in order to ensure compliance of a product to the client's product specifications.}
\item {Due to the slight language barrier, it highlighted the importance of good and well-defined instruction and communication to clearly convey the client’s needs.}
\item {Worked on electronically enhanced hearing and protection devices, with both hardware and software related problems issues, such as poor isolation of key electronic parts causing feedback and software induced feedback.}
\end{cvitems}
}

%------------------------------------------------    




\end{cventries}