%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{$\sim$/extracurricular\_activity/}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Best Web-App Winner} % Affiliation/role
{Royal Hackaway} % Organization/group
{Royal Holloway, University of London} % Location
{Jan. 2022} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Won `Best Web-App' and finished top 5 overall.}
\item {Participated in a 26 hour national hackathon in a team of two.}
\item {Developed a Svelte web-app with a Python machine learning back-end to predict the weight of an unborn child based on antinatal datapoints.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Black Belt/Registered Instructor} % Affiliation/role
{Guba Doce Pares \tiny{(Eskrima-Kali-Arnis; a Filipino stick and dagger martial art)}} % Organization/group
{London, UK} % Location
{2014 - Present} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {National men's open close quarters champion, single and double stick national champion, and single stick international champion.}
\item {As a senior member, I spent many years teaching younger members of the club.}
\item {As a registered instructor, I am looking to set up my own club in the near future.}
\end{cvitems}
}


%------------------------------------------------

\cventry
{Team Captain} % Affiliation/role
{RHUL Esports} % Organization/group
{Royal Holloway} % Location
{2019 - 2022} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Led the Overwatch esports teams, overseeing both GameSoc events and national tournament entries due to my active contributions to the team as a top 100 player in Europe.}
\item {Our team had multiple top 5 finishes in national leagues.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Young Leader} % Affiliation/role
{Old Elthamians} % Organization/group
{Bromley, UK} % Location
{2014 - 2018} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Coached young members of the club, and scoring and umpiring all ages games.}
\item {Awarded a Jack Petchey award for my contributions to the cricket club through the young leaders’ programme.}
\end{cvitems}
}



\end{cventries}